AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-13 chapters/05-discussion.tex
Add stress tests discussion

>>>>

The resilience tests were aimed at testing the reliability of the \acrlong{fec}
algorithm used in the radio protocol's frame layer. Those tests were considered
critical because the frame layer must provide reliability to the
\acrshort{ahabus} radio protocol. Since the chosen \acrshort{fec} algorithm,
Reed-Solomon codes $RS(255,223)$, can fix a maximum of 16 bytes per 256-byte
code block, the tests were designed to simulate average error rates below (8
bytes out of 256), near (14 bytes out of 256) and above (18 bytes out of 256
that theoretical limit, through the software method discussed in section
\ref{ssec:method-resilience}.

Overall, figures \ref{fig:stress-8.256}, \ref{fig:stress-14.256} and
\ref{fig:stress-18.256} show the expected behaviour: the higher the average
error rate, the more erroneous frames. It is interesting to note that even at
the two lower rates ($\frac{8}{256}$ and $\frac{16}{256}$), which are below
the maximum rate that the \acrlong{ecc} should be able to fix, some frames are
dropped. The main cause is the use of start sequences. While \acrshort{ecc} are
able to correct up to 16 erroneous bytes, the detection of the frame itself is a
pre-requisite. If the frame start marker itself is corrupted, the decoder cannot
identify the frame, and it will is counted as lost, even if the total number
of erroneous bytes in the frame is less than 16.

Additionally, it is important to note that the target error rates were averages.
For those three tests, the code used was set to corrupt the current byte if a
pseudo-random number between 0.0 and 1.0, obtained through the C standard
library's \texttt{rand()} function, was above the error rate. \texttt{rand()},
while allowing a good estimate, is not statistically accurate, and some frames
had a higher or lower than average erroneous bytes. This is believed to be the
source of the discrepancy between the theoretical average error rates and the
actual correction rates shown for the first two tests in table
\ref{tab:stress-fec}.

Finally, the third tests demonstrates the inaptitude of the \acrshort{ecc}
to cope when the average error rate is above the the algorithm's maximum. Most
of the frames were lost, the only few decoded being just under the threshold
due to the fluctuations discussed above. Table \ref{tab:stress-fec} shows that
the correction rate is significantly lower than the $\frac{14}{256}$ test, which
was expected: Reed-Solomon codes cannot fix even some errors if the number of
erroneous bytes in a code block is above the chosen algorithm's limit.

Overall, these three tests showed that the \acrshort{fec} algorithm chosen for
the frame layer worked as expected, so long as the error rate remains under
16 bytes per code block (frame). Ultimately, this limit is a trade-off between
reliability and bandwidth: raising it would require more bytes in each frame
to be allocated to \acrlong{ecc}.
